Quantitative Benchmarking for Automatically Generated Conjectures

### 2018-05-22 TEBenchmarkPaper/article.tex
TEB tweaks (from Jianguo)

\begin{abstract}
  We propose a benchmarking methodology to evaluate the efficiency and quality
  of \emph{conjecture generation} by automated tools for \emph{mathematical
    theory exploration}. Our approach uses widely available theorem proving
  tasks as a \emph{ground-truth} corpus, and we demonstrate its use on the
  QuickSpec and IsaCoSy tools. We found that both may fail, even for small
  inputs, but QuickSpec usually finishes in significantly less time than IsaCoSy
  and produces significantly more ``interesting'' output. By providing a
  standard, cross-tool evaluation technique we allow the disparate approaches
  currently being pursued to be more directly compared. Our hope is to encourage
  innovation and improvements similar to those seen in fields like automated
  theorem proving, where the availability of benchmarks encourages healthy
  competition.
%\keywords{First keyword \and Second keyword \and More}
% \PACS{PACS code1 \and PACS code2 \and more}
% \subclass{MSC code1 \and MSC code2 \and more}
\end{abstract}

>>>>

\begin{abstract}
  We propose a benchmarking methodology to evaluate the efficiency and quality
  of \emph{conjecture generation} by automated tools for \emph{mathematical
    theory exploration}. Our approach uses widely available theorem proving
  tasks as a \emph{ground-truth} corpus, and we demonstrate its use on the
  QuickSpec and IsaCoSy tools. We found that both may fail, even for small
  inputs, but QuickSpec usually finishes in significantly less time than IsaCoSy
  and produces significantly more ``interesting'' output. By defining a standard
  benchmark we provide a measure of progress for the field, encourage
  innovation through healthy competition and allow direct comparisons to be made
  between the disparate approaches currently being pursued for this task.
%\keywords{First keyword \and Second keyword \and More}
% \PACS{PACS code1 \and PACS code2 \and more}
% \subclass{MSC code1 \and MSC code2 \and more}
\end{abstract}
